### 2021-09-10 README.Rmd
Modified getdata to include NAS data. New saurecdevs plot. NO EWN

@@

* 2021-08-23 aMSE 0.0.0.300 Using text as SAU names in the control file now labels all plots and those labels are not included in the tables. glb$saunames now contains the text labels. Other changes include generalizing the number of plots to match number of SAU in all cases (I hope), There is also, now, a ConstantCatchHS.R file in the data-raw sub-directory that allows for a constant catch to be applied to each SAU. This demonstrates that the issue when using the TasmanianHS.R file is not the aMSE package but how the Tasmanian HS functions work with the available data.

@@

# HarvestStrategy.R should also be in rundir
source(paste0(rundir,"/TasmanianHS.R"))
# run the scenario --------------------- Obviously unhash this to make it work
#
# out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,hcrfun=mcdahcr,
#               sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
#               getdata=tasdata,calcpopC=calcexpectpopC,makeouthcr=makeouthcr,
#               varyrs=7,startyr=48,cleanslate=TRUE,verbose=TRUE,
#               ndiagprojs=4,savesauout=TRUE)
# 
# makeoutput(out,rundir,datadir,postfixdir,controlfile,openfile=TRUE,verbose=FALSE)

>>>>

* 2021-09-10 aMSE 0.0.0.100 Many small, but significant, changes. Modified getdata which interacts with the ###HS.R file and added the
zoneDP$NAS data input. Added a summary recdev plot to condition tab.

@@

@@

# HarvestStrategy.R should also be in rundir
source(paste0(rundir,"/TasHS1_Tas.R"))
# run the scenario --------------------- Obviously unhash this to make it work
#
# out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,hcrfun=mcdahcr,
#               sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
#               getdata=tasdata,calcpopC=calcexpectpopC,makeouthcr=makeouthcr,
#               varyrs=7,startyr=48,cleanslate=TRUE,verbose=TRUE,
#               ndiagprojs=4,savesauout=TRUE)
# 
# makeoutput(out,rundir,datadir,postfixdir,controlfile,openfile=TRUE,verbose=FALSE)
